%---------------------------------------------------------------------------
% Abstract

\begin{abstract}
 \addcontentsline{toc}{chapter}{Abstract}
 
 This work investigates the gain saturation of a novel optically-pumped vertical external cavity surface emitting laser (VECSEL) operating in the 2-\unit{\um} spectral range with an integrated DBR for the pump wavelength. This new design, with the integrated pump DBR, showed significant improvement in continuous wave operation but was limited in modelocked operation. To investigate this behaviour, the gain saturation was measurement to check for any indication of this behaviour. For this, the measurements were conducted for three different heat sink temperatures of \qtylist{-10;0;10}{\celsius} and for different VECSEL designs. We compare the saturation fluence, small signal reflectivity and rollover parameter obtained from fitting the measurement data with a model based on the saturable absorption of SESAMS, to other similar structures. 

 The results demonstrates record small signal gain of 6.5\% as well a significant difference in rollover parameter compared to older designs, signifying further investigation into the rollover parameter is needed to solve the challenge of improving the modelocked operation of the novel design. 

 Additionally, we automated the pump power control in the experimental setup, leading to an increased time efficiency and unattended measuring capability. For this the signal processing algorithm was improved, addressing previous limitations during measuring requiring restarting of the measurement. The updated algorithm utilized a lowered triggering value, examination of neighboring points, and considered signal trends to ensure an accurate trigger of the data evaluation. 
\end{abstract}
 % \cleardoublepage


%---------------------------------------------------------------------------
% Acknowledgements

% \chapter*{Acknowledgements}
%  \addcontentsline{toc}{chapter}{Acknowledgements}

% Write acknowledgements here

 % \cleardoublepage

%---------------------------------------------------------------------------
% Table of contents

 \setcounter{tocdepth}{4}
 \tableofcontents

 \clearpage

%---------------------------------------------------------------------------
% Symbols

% \chapter*{Acronyms and Abbreviations}\label{chap:symbole}
%  \addcontentsline{toc}{chapter}{Acronyms and Abbreviations}


% \begin{tabbing}
%  \hspace*{3.2cm}  \= \kill

% write abbreviations like this\\
% ET\> Evapotranspiration\\



% \end{tabbing}

 % \cleardoublepage

%---------------------------------------------------------------------------
